Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-07-04 prop_letter.tex
prop.tex @Book{HuberRonchetti2009} Added...

We will start by reviewing IVPMs in the classical setting\nb\citep{JamisonLodwick2004,Galvan2008}
and then propose our quantum generalization. In the classical setting,
there are several proposals for ``imprecise probabilities\nb\citep{Dempster1967,Artstein1972,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Galvan2008,Grabisch2016}.''
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event $E$ is generalized
from a single real number to an interval of certainty $[\ell,r]$
where\nb$\ell$ intuitively corresponds to the strength of evidence
for the event and $r$ corresponds to the strength of evidence against
the event. The collection of intervals used in the definition of a
probability measure must satisfy certain properties which we explain
next.

>>>>

We will start by reviewing IVPMs in the classical setting
and then propose our quantum generalization. In the classical setting,
there are several proposals for ``imprecise
probabilities\nb\citep{Dempster1967,Artstein1972,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Galvan2008,HuberRonchetti2009,Grabisch2016}.''
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event $E$ is generalized
from a single real number to an interval of certainty $[\ell,r]$
where\nb$\ell$ intuitively corresponds to the strength of evidence
for the event and $r$ corresponds to the strength of evidence against
the event. The collection of intervals used in the definition of a
probability measure must satisfy certain properties which we explain
next.
